\begin{rubric}{Publications}
\entry*[2018]%
P. Gentine, M. Pritchard, S. Rasp, G. Reinaudi \& G. Yacalis
\par{
\emph{Could machine learning break the convection parameterization deadlock?}
\par{
Geophysical Research Letters,  \textbf{45}, 5742
}}%
%
\entry*[2012]%
G. Reinaudi, C. B. Osborn, M. McDonald, S. Kotochigova \& T. Zelevinsky
\par{
\emph{Optical Production of Stable Ultracold Sr$88$ Molecules}
\par{
Phys. Rev. Lett.,  \textbf{109}, 115303 (2012)
}}%
%
\entry*[2012]%
G. L. Gattobigio, A. Couvert, G. Reinaudi, B. Georgeot \& D. Guéry-Odelin
\par{
\emph{Optically guided beam splitter for propagating matter waves}
\par{
Phys. Rev. Lett.,  \textbf{109}, 030403 (2012)
\par{Selected for the \textit{American Physical Society \textbf{"Spotlighting exceptional research"}}}
}}%
%
\entry*[2011]%
G. Reinaudi, C. B. Osborn, K. Bega, \& T. Zelevinsky
\par{
\emph{Dynamically configurable and optimizable Zeeman slower using permanent magnets and servomotors}
\par{
J. Opt. Soc. Am. B, 160242 (2011)
}}%
%
\entry*[2010]%
G. Reinaudi, book publication of the Ph.D. Thesis 
\par{
\emph{Manipulation d'atomes ultra-froids: vers un laser à atomes continu 
  \ifthenelse{\equal{\EnQuelleLangue}{\EnAnglais}}{ (Manipulation of ultra cold atoms: towards a continuous atom laser)}{}
}
\par{
Editions Universitaires Europeennes, ISBN 978-613-1-50940-7 (2010)
}}
%
%
\entry*[2008]%
A. Couvert, M. Jeppesen, T. Kawalec,  G. Reinaudi, R. Mathevet, \& D. Guéry-Odelin 
\par{
\emph{Quasi-monomode guided atom laser}
\par{
Eur. Phys. News \textbf{39-\textit{Highlights}}, 6-14 (2008)
}}
%
%
\entry*[2008]%
A. Couvert, M. Jeppesen, T. Kawalec, G. Reinaudi, R. Mathevet,  \& D. Guéry-Odelin
\par{
\emph{A quasi-monomode guided atom-laser from an all-optical Bose-Einstein condensate}
\par{
Europhys. Lett. \textbf{83}, 50001 (2008)
\par{Selected for the \textbf{\textit{"Highlights"}} section in Eur. Phys. News \textbf{39}}
}}
%
%
\entry*[2008]%
G. Reinaudi \& D. Guéry-Odelin
\par{
\emph{A Maxwell's demon in the generation of an intense and slow guided beam}
\par{
Phys. Rev. A \textbf{78}, 015401 (2008)
}}
%
%
\entry*[2008]%
A. Couvert, T. Kawalec, G. Reinaudi \& D. Guéry-Odelin
\par{
\emph{Optimal transport of ultracold atoms in the non-adiabatic regime}
\par{
Europhys. Lett. \textbf{83}, 13001 (2008)
}}
%
%
\entry*[2007]%
G. Reinaudi, T. Lahaye, Z. Wang \& D. Guéry-Odelin
\par{
\emph{Strong saturation absorption imaging of dense clouds of ultracold atoms}
\par{
Opt. Lett. \textbf{32}, 3143  (2007)}}
%
%
\entry*[2007]%
G. Reinaudi, A. Sinatra, A. Dantan \& M. Pinard
\par{
\emph{Squeezing and entangling nuclear spins in $^3$He}
\par{
J. Mod. Opt. \textbf{54}, 675-695 (2007)
}}
%
%
\entry*[2007]%
G. Reinaudi, Z. Wang, A. Couvert, T. Lahaye \& D. Guéry-Odelin
\par{
\emph{A mirror to generate a beam}
\par{
Eur. Phys. News \textbf{38-\textit{Highlights}}, 3-17 (2007)
}}
%
%
\entry*[2006]%
G. Reinaudi \& D. Guéry-Odelin
\par{
\emph{The atom lasers}
\par{
DGA Edition, Bulletin bibliographique \textit{Prospective Oriented Group on Lasers and Optronics (POLOQ)}
\par{n°2006-1, p. 165-172}
}}
%
%
\entry*[2006]%
G. Reinaudi, Z. Wang, A. Couvert, T. Lahaye \& D. Guéry-Odelin
\par{
\emph{A moving magnetic mirror to slow down a bunch of atoms}
\par{
Eur. Phys. J. D \textbf{40}, 405-410 (2006)
\par{Selected for the \textit{\textbf{"Highlights"}} section in Eur. Phys. News \textbf{38}
}}}
%
%
\entry*[2006]%
T. Lahaye, G. Reinaudi, Z. Wang, A. Couvert \& D. Guéry-Odelin
\par{
\emph{Transport of Atom Packets in a Train of Ioffe-Pritchard Traps}
\par{
Phys. Rev. A \textbf{74}, 033622 (2006)
}}
%
%
\entry*[2006]%
G. Reinaudi , T. Lahaye , A. Couvert, Z. Wang \& D. Guéry-Odelin
\par{
\emph{Evaporation of an atomic beam on a material surface}
\par{
Phys. Rev. A \textbf{73}, 035402 (2006)
}}
%
%
\entry*[2005]%
T. Lahaye, Z. Wang, G. Reinaudi, S.P. Rath, J. Dalibard \& D. Guéry-Odelin
\par{
\emph{Evaporative cooling of a guided rubidium atomic beam}
\par{
Phys. Rev. A \textbf{72}, 033411 (2005)
}}
%
%
\entry*[2005]%
T. Aichele, V. Zwiller, M. Scholz, G. Reinaudi, J. Persson \& O. Benson
\par{
\emph{Multiplexed quantum cryptography with single InP quantum dots}
\par{
Proceedings of SPIE \textbf{5722}, 30-44 (2005)
}}
%
%
\entry*[2005]%
A. Dantan, G. Reinaudi, A. Sinatra, F. Laloë, E. Giacobino \& M. Pinard
\par{
\emph{Long lived quantum memory with nuclear atomic spins}
\par{
Phys. Rev. Lett. \textbf{95}, 123002(2005)
}}
%
%
\entry*[2004]%
T. Aichele, G. Reinaudi \& O. Benson
\par{
\emph{Separating cascaded photons from a single quantum dot: Demonstration of multiplexed quantum cryptography}
\par{
Phys. Rev. B \textbf{70}, 235329 (2004)
}}
%

\end{rubric}
