\begin{rubric}{Skills}
\noentry{2007-2013}
\subrubric{AI, Machine Learning \& LLM:}
\entry*[]%
Expertise in usage/application of Large Language Models (LLM), LLMOps, AI Agents workflows, Cursor.
\entry*[]%
Extensive and original experience with deep learning architectures applied to financial data.
\entry*[]%
Skilled in implementing modern AI frameworks: LangGraph, LlamaIndex, Agentic systems, local LLMs, etc.
\entry*[]%
Expertise in MLOps, AI-driven workflows, and Generative AI tools for coding, testing, documenting, etc.
\entry*[]%
Experienced with adapting new paradigms and cutting-edge AI research to solve complex problems in new ways.
%
\subrubric{Quantitative Finance:}
\entry*[]%
Strong logical skills, innate curiosity, quick at grasping complex problems, and proposing innovations.
\entry*[]%
Low-latency trading, order book market data, code optimization, backtesting, Series 57 current.
\entry*[]%
Experienced with research-grade evolutionary optimizations, AI-powered trading strategies.
\entry*[]%
Skilled at adapting recent research-grade papers and codebases to address new challenges. 
%
%
\subrubric{Programming:}
\entry*[]%
Python: \underbar{Highly} proficient, Top 0.6\% Python Code Expert (Legend League in coding competitions).
\entry*[]%
Advanced Python: asyncio, generators, type safety, Pydantic, testing, FastAPI, Polars,...
\entry*[]%
C++: Experienced with large codebases in both HFT firm environment and personal projects. 

Familiar with Meta-programming, branch prediction, cache warming, static polymorphism (CRTP),...
\entry*[]%
Tools: Proficient user of TensorFlow, PyTorch, Pandas, Polars, Hasura, Django, GraphQL, Linux, Docker, Kubernetes, GCP, CI/CD, Git, Jupyter, Elastic Search,...
%
\subrubric{Personal:}
\entry*[]%
Licensed Pilot with Instrument Rating: Advanced aviation qualification demonstrating technical mastery, methodical decision-making, and commitment to excellence.
\entry*[]%
Rapid problem assimilation: Ask sharp questions early to quickly "see the whole picture."
%
\end{rubric}
