\begin{rubric}{Professional Experience}
\subrubric{Technology Startup and Machine Learning:}
\entry*[2021-2024]%
\textbf{Sinecue.AI (New York):} CTO and Co-Founder
\par{Developed the entire codebase and infrastructure of the company using Python and GCP.}
\par{Built and led a cost-efficient team of remote developers.}
\par{Planned technology adoptions and integrated state-of-the-art ML techniques.}
%
\subrubric{Algorithmic Trading / Data Science:}
\entry*[2018-2021]%
\textbf{JPMorgan (New York):} Data Scientist Manager, VP
\par{Established the data science platform and the prediction ecosystem for the Roar group.}
%
\entry*[2015-2018]%
\textbf{Ronin Capital (New York):} Lead Data Scientist, Lead Strategy Developer
\par{Adapted state-of-the-art research tools into production trading strategies (equity/ETF).}
\par
  {\renewcommand{\arraystretch}{1}%
    \begin{tabular}{>{}l<{}@{\hspace{5pt}}%
    p{.002\textwidth}}
      $\diamond$~~Adapted very recent deep-learning papers to identify/optimize trading signals. \\
      $\diamond$~~Developed various programs to route and react to the inferred signals. \\
      $\diamond$~~Implemented an Order Management System for production trading. \\
    \end{tabular}%
   }
%
\entry*[2013-2015]%
\textbf{Global Trading Systems (New York):} Lead Trading Model Developer
\par{Coded the full trading logic, conducted backtesting, and analysis (fixed income).}
\par
  {\renewcommand{\arraystretch}{1}%
  \begin{tabular}{>{}l<{}@{\hspace{5pt}}%
    p{.002\textwidth}}
      $\diamond$~~Researched and implemented low-latency strategies for HFT market-making clients. \\
      $\diamond$~~Created a fully automated strategy deployment system. \\
    \end{tabular}%
    }
%
\subrubric{Framework for Visually Interactive Research, Trading, and Optimization:}
\entry*[2007-2013]%
Project \emph{single-handedly} designed and developed.
\par{Initially used by Columbia University for experiments, adapted for production trading at Ronin Capital.}
\par
  {\renewcommand{\arraystretch}{1}%
  \begin{tabular}{>{}l<{}@{\hspace{5pt}}%
    p{.002\textwidth}}
      $\diamond$~~Developed in C++, object-oriented programming, with highly interactive GUI, and multi-threading. \\
      $\diamond$~~Supported over 30+ plugins, developed by users through an exposed API. \\
      $\diamond$~~Featured interfaces for image processing, data fitting, scripting, genetic optimizations, and trading. \\
    \end{tabular}%
    }
%
\subrubric{Hands-on Experimental Research:}
\entry*[2008-2013]%
\textbf{Columbia University (New York):} Postdoc and Associate Research Scientist in Atomic Physics
\par{Built from scratch an entire quantum physics experiment.}
%
\entry*[2004-2008]%
\textbf{\'Ecole Normale Sup\'erieure de Paris:} Ph.D. in the Laboratoire Kastler-Brossel
\par{Built highly original apparatus for \emph{ultra-cold atoms} quantum physics.}
%
\subrubric{Teaching:}
\entry*[2006-2008]%
Scientific expert demonstrator at the \emph{Palais de la D\'ecouverte} (scientific museum) in Paris.
%
\entry*[2004-2005]%
Examiner in preparatory classes for the Grandes \'Ecoles.
\end{rubric}
